Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-07-28 Documents/Paper/ms.tex
Caption

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{sinewaves_likelihood.pdf}
\caption{The inference for $N$, the number of sinusoids, based on the
sinusoid data. The true value was $N=2$.
\label{fig:sinewaves_likelihood}}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{sinewaves_likelihood.pdf}
\caption{{\bf Top panel: }
The shape of the likelihood function with respect to prior mass.
{\bf Bottom panel: }The posterior weights of the saved samples. The existence
of a phase transition causes this to display two separate peaks, which
would be difficult to mix between if we simply attempted to sample the posterior
distribution.
\label{fig:sinewaves_likelihood}}
\end{center}
\end{figure}
